---
title: "write_functions"
author: "Courtney Johnson"
date: "October 25, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
library(p8105.datasets)
library(httr)
library(viridis)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```


## Let's write some functions

start small!

```{r}
x = rnorm(25, 5, 3)

(x - mean(x)) / sd(x)
```


Write a function to compute z scores for a vector.

```{r}
z_scores = function(x) {
  
  (x - mean(x)) / sd(x)
  
}
```


Check to see if this works...

```{r}
unif_sample = runif(100)

z_scores(unif_sample)
```

Check the following examples


```{r, error = TRUE}
z_scores(3)
z_scores("my name is Jeff")
z_scores(iris)
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

Put in some checks on inputs

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  (x - mean(x)) / sd(x)
}
```

Check again...
```{r, error = TRUE}
z_scores(3)
z_scores("my name is Jeff")
z_scores(iris)
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```


### Mean and standard deviation

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  tibble(
    mean_x = mean(x),
    sd_x = sd(x)
    
  )
}
```


```{r}
mean_and_sd(unif_sample)
```


## Multiple inputs 

Look at simple linear regression!

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```


Write a function that simulates, fits the model, and returns the estimates. Inputs are sample size and true coefficients.


```{r}
sim_regression = function(n, beta0, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )

  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
  
}
```


```{r}
sim_regression(n = 3000, beta0 = 0, beta1 = -1)
```


## Revisit Amazon data

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


Now write a function for this

```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  review_titles = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
}

read_page_reviews(url)

url2 = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

read_page_reviews(url2)
```



Let's extract a lot of reviews

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(urls[1]),
  read_page_reviews(urls[2]),
  read_page_reviews(urls[3]),
  read_page_reviews(urls[4]),
  read_page_reviews(urls[5])
)
```


Revisit LotR data

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = tolower(race)) %>% 
  select(movie, everything())
```

Try to write a function to do this

```{r}
lotr_import = function(cell_range, movie_title) {
  
  df = readxl::read_excel("./data/LotR_Words.xlsx", range = cell_range) %>%
    mutate(movie = movie_title)
  
  df
  
}

lotr_import(cell_range = "B3:D6", movie_title = "fellowship_ring")
lotr_import(cell_range = "F3:H6", movie_title = "two_towers")
lotr_import(cell_range = "J3:L6", movie_title = "return_king")
```


